Fast gravitational wave parameter estimation without compromises

### 2023-02-06 src/tex/ms.tex
Add rift and extra sentence in discussion to avoid swelling in discussion

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot,Lee:2022jpn}. While these avenues are promising for
standard GW problems, they rely on assumptions that may not hold for analyses
targeting additional physical effects beyond standard CBCs in GR, such as
lensing and deviations from GR, or may use approximations that do not compute
the Bayesian likelihood exactly.

@@

% Compared to other works
There have been several recent efforts to speed up GW parameter estimation,
relying on techniques ranging from efficient reparameterizations
\cite{Islam:2022afg,Roulet:2022kot, Lee:2022jpn} to deep learning
\cite{Dax:2021tsq,Dax:2022pxd}. While all of these methods can achieve
minutes-scale parameter estimation with high fidelity under some conditions,
our approach possesses unique strengths, and may complement some of those other
techniques.

>>>>

% Effort going to new tools development.
In order to address this, there are efforts from multiple groups to speed up the
PE process. This includes methods that employ modern techniques such as
leveraging adaptive proposal distribution in nested sampling
\cite{Williams:2021qyt}, deep learning networks pre-trained on large collections
of waveforms \cite{Dax:2021tsq,Dax:2022pxd}, as well as methods that reduce the
computational expense of classical PE by leveraging our knowledge of GW signals
\cite{Islam:2022afg,Roulet:2022kot,Lee:2022jpn,Lange:2018pyp,Wofford:2022ykb}.
While these avenues are promising for standard GW problems, they rely on
assumptions that may not hold for analyses targeting additional physical effects
beyond standard CBCs in GR, such as lensing and deviations from GR, or may use
approximations that do not compute the Bayesian likelihood exactly.

@@

% Compared to other works
There have been several recent efforts to speed up GW parameter estimation,
relying on techniques ranging from efficient reparameterizations
\cite{Islam:2022afg,Roulet:2022kot} to deep learning
\cite{Dax:2021tsq,Dax:2022pxd}. While all of these methods can achieve
minutes-scale parameter estimation with high fidelity under some conditions, our
approach possesses unique strengths, and may complement some of those other
techniques. There are more attempts
\cite{Lee:2022jpn,Wofford:2022ykb,Lange:2018pyp,Williams:2021qyt,Morisaki:2021ngj}
in speeding up GW parameter estimation, here we discuss the most relevant twos
in the context of our work.
